%-------------------------
% Resume in Latex
% Author : Abhishek Chandragiri
% License : MIT
%------------------------



\documentclass[letterpaper,10.8pt]{article}



\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}




\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}



% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}



\urlstyle{rm}



\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}



% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]



%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}



\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}



\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}




\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}



\renewcommand{\labelitemii}{$\circ$}



\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%




\begin{document}



%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Abhishek Chandragiri}} & Email : \href{mailto:abhishek.intern0323@gmail.com}{abhishek.intern0323@gmail.com}\\
  \href{https://www.linkedin.com/in/abhishek-chandragiri/}{Linkedin: https://www.linkedin.com/in/abhishek-chandragiri/} & Phone : 281-857-9658 \\  
\href{https://github.com/Abhi0323}{Github: https://github.com/Abhi0323} \\
\href{ https://abhi0323.github.io/Abhishek-Chandragiri-Portfolio/}{Portfolio: https://abhi0323.github.io/Abhishek-Chandragiri-Portfolio/}
\end{tabular*}


\end{tabular*}
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Houston}{Houston, TX}
      {Masters in Data Science;  GPA: 3.60}{Jan 2022 - Dec 2023}
      
       % {\scriptsize \textit{Courses: Machine Learning, Database Management System, Big Data Analytics, Business intelligence, Probability and Statistics, Digital Image Processing, Data Analytics for Constructional Management, Data Analytics for Engineering Management.}}
        
    \resumeSubheading
      {TKR College of Engineering and Technology}{Hyderabad, India}
      {Bachelor of Electronics and Communication Engineering;  GPA: 3.5}{Aug 2017 - July 2021}
  \resumeSubHeadingListEnd



%
%--------PROGRAMMING SKILLS------------
\section{Skills Summary}
    \resumeSubHeadingListStart
    \resumeSubItem{Skills, Technologies, and Libraries}{SQL, Python, Machine Learning, Tableau, Power BI, Time Series Analysis, MySQL Workbench, Oracle SQL Developer, SQLite Excel, Microsoft Office Suite, GitHub, LaTeX, Pandas, Numpy, Scikit-learn, Matplotlib, Seaborn, Tibco-Spotfire, CrowdStrike, Splunk, Jupyter Notebook, Google Analytics.}
    \resumeSubItem{Areas of Interest}{ Artificial Intelligence, Data Management, Cloud Computing, Cybersecurity, Robotics, Digital Marketing, Financial Analysis, Healthcare Analytics, Business Analytics, Predictive Analytics, Computer Vision. }
\resumeSubHeadingListEnd





%-----------EXPERIENCE-----------------

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Vulcan Materials Company}{Alabama, Birmingham - Remote }
    {Data Analyst - Internship}{May 2023 -  Current}
    \resumeItemListStart
        \item{Processed and analyzed millions of data points from CrowdStrike using Python, Falcon API, and SQL in Jupyter Notebook. This analysis led to the identification of key vulnerabilities, improving overall security posture through targeted remediation efforts.}
        \item{Utilized advanced SQL queries to extract key insights from complex database structures, effectively communicating findings to technical and non-technical stakeholders. Designed interactive Power BI dashboards for real-time data analysis, enabling stakeholders to monitor KPIs and drive impactful business strategies.}
      \resumeItemListEnd
    \resumeSubheading
    {University of Houston}{Houston, TX}
    {Graduate Instructional Assistant - Data Analytics}{Feb 2022 -  May 2023}
    \resumeItemListStart
        \item{Created detailed reports on student performance for different data science courses. Graded papers, analyzed data, and produced useful lecture documents. This work helped improve the quality of teaching and learning.}
        \item{Collected and analyzed data as needed by the program director. Used data analysis to find important insights. Also, performed database queries to find specific applicant data, helping to pick the best applicants more effectively.}
      \resumeItemListEnd
    \resumeSubheading
    {Veniso Solutions India Pvt Ltd}{Hyderabad, India} {Data Analyst - Internship}{March 2021 - Dec 2021} \resumeItemListStart 
    \item{Employed Python libraries (Pandas, Matplotlib, Seaborn, Scikit-Learn) for extensive data preprocessing, exploratory analysis, and machine learning model development. Uncovered patterns and correlations, empowering informed decision-making and strategic planning.}
    \item {Utilized advanced SQL queries to extract key insights from complex database structures, effectively communicating findings to technical and non-technical stakeholders. Designed interactive Power BI dashboards for real-time data analysis, enabling stakeholders to monitor KPIs and drive impactful business strategies.}
    
    \resumeItemListEnd
\resumeSubHeadingListEnd



%-----------PROJECTS-----------------
\section{Academic Projects}
\resumeSubHeadingListStart
\resumeSubItem{Letter Recognition (Python Programming, Machine Learning)\href{https://github.com/Abhi0323/LetterRecognition_Project}{(View Project)} } 
\resumeItemListStart
        \item {Classified letter recognition dataset with various algorithms (KNN, SVM, Random Forest, Logistic Regression) to find the best model that precisely recognizes capital letters and achieved an accuracy of 96\% with the SVM algorithm.}
        \item{Performed hyper parameter tuning on all the algorithms and visualized their outputs with default parameters and final hyper parameter tuned outputs, resulting in a more accurate model.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\resumeSubHeadingListStart
\resumeSubItem{Phishing Website Detection (Python Programming, Machine Learning)\href{https://github.com/Abhi0323/Phishing-Website-Detection}{(View Project)} } 
\resumeItemListStart
        \item {Developed a machine learning model to detect phishing websites with a 97.1\% accuracy rate, using preprocessing techniques and Scikit-learn libraries.}
        \item{Utilized various classification algorithms such as Logistic Regression, Decision Tree, Random Forest, and SVM to identify the most efficient model.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\resumeSubHeadingListStart
\resumeSubItem{Covid-19 Data Analysis (Excel, SQL, Tableau)\href{https://github.com/Abhi0323/Covid19_Data_Analysis}{(View Project)}}
\resumeItemListStart
        \item{Explored the processed data using SQL in order to identify any patterns or relationships and discovered that there was a positive correlation between the number of confirmed cases and the number of deaths.}
        \item{Created Tableau visualizations on the covid 19 data set to get an overview of the global spread of the virus, as well as more detailed views of specific countries and regions.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
\end{description}
%-------------------------------------------
\end{document}
